%!TEX root = these.tex

\begin{acknowledgements}

I would like to thank everyone who helped me complete my degree.

First I would like to express my sincere appreciation to my director \textbf{Professor Sylvain Hallé} for his supervision, support, patience and generosity. I was very lucky to have a supervisor who cares so much about students and who is always patient for every kind of questions and problems. Before I entered the department, I had never imagined that as a foreign MSc. student, I could have the chance of receiving scholarships and taking part in the work of paper writing for real journals and conferences. It was \textbf{Professor Sylvain Hallé} who granted me the opportunities and confidence. Thanks to him, I have a fantastic memory in UQAC.

I would like to express my gratitude to \textbf{Professor Sylvain Boivin} for his guidance, support and help. He motivated me to return to university for a Master degree, encouraged me for my French learning and introduced me to \textbf{Professor Sylvain Hallé}.

I would like also to thank \textbf{Mme. Marjolaine Hénault} for her kindness, generosity, encouragement and great help for my French learning, friends living in Chicoutimi: \textbf{Ran Wei, Ping Li, Jian Qin et al.} for their friendship, encouragement, support and help, all staff of \textbf{l'École de langue française} for teaching me French, friends and students working in LIF: \textbf{Edmond la Chance, Francis Guérin, Daehli Nadeau-Otis et al.} for their friendship and support.

At last, I would like to express my warmest thanks to my wife \textbf{Moon Ji Hyun}, whose companionship, selfless dedication, encouraging words and best cooking technique on earth were the essential motivation of the completion of my Master.

\end{acknowledgements}